Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-22 MS_thesis.tex
Rephrase acknowledgements

%The acknowledgements go here.
\acknowledgments{
%\vspace{-0.5cm}
First and foremost, I am grateful to my advisors, Prof. Vishwesha Guttal and Prof. Rohini Balakrishnan, for their masterful mentoring. The enormous academic freedom they gave me to pursue essentially whichever ideas seemed promising at the time, coupled with their readiness to provide detailed guidance whenever I asked for it, made working with them an incredibly enriching experience. Their constant focus on the bigger picture was vital to helping me see the forest when I was stuck looking at the trees. Both Vishu and Rohini are brilliant scientists and fantastic mentors, and their mentorship and guidance have deeply impacted my ways of thinking about science and mentoring. I am also grateful to all the members of the \href{https://teelabiisc.wordpress.com/}{Theoretical Ecology and Evolution lab} and the \href{https://sites.google.com/view/rohinibalakrishnanlab/home}{Animal Communication and Bioacoustics Lab} for providing a supportive and productive working environment.

I would also like to thank Prof. Sutirth Dey, my expert for this project. Sutirth provided constructive comments during the mid-year evaluation that helped me re-evaluate my project and its goals. Sutirth's brilliant course on evolution at IISER and various fascinating conversations with him and other lab members during my time as an intern at the \href{https://sites.google.com/a/acads.iiserpune.ac.in/sdlab/pbl-iiser-p}{Population Biology Lab} have been instrumental in shaping my thoughts on evolution.

I am grateful to many friends who made the IISER journey enjoyable. Countless long days and nights with Adithyan, Abhishek, Arjun, Chebi, Gaurav, Harshit, Manas, Milie, and Shruthi, have greatly helped me grow as a person, both intellectually and emotionally. I love all of y'all. Arjun has always been a great sounding board for my thoughts, no matter how inane, and has been very patient and supportive in more ways than I could list here. Milie is the occasional fitness friend that everyone needs, and occasionally texting her encouraged me to hit the gym at least semi-regularly even during hectic parts of the thesis project when schedules were uncertain. I am indebted to our D\&D group in general and Manas in particular for introducing me to D\&D and Critical Role, both of which were very helpful in getting through the pandemic as well as the thesis. Shruthi is a constant source of cat related mental health boosts and has more generally taught me a lot about a lot during my time at IISER. I am also grateful to Abhishek for letting me bother him with various physics-related questions throughout the project year. I entered this project as someone who knew some mathematics and some biology but quickly realized I would benefit from reading physics papers (typically written in physics language). Abhishek patiently answered all my basic questions about physics language/tools and skillfully helped me understand how physicists think. Insightful conversations about evolution with Gaurav were formative in gaining fresh perspectives on various topics. Closer to home, Akshay and Prerana have been my closest friends since high school and continue to provide unerring and unconditional love and support. I don't know where I would be without them today.

@@

Finally, I am eternally indebted to my parents, Raja and Vidya. They have quite literally supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest  with virtual strangers and no cellular network, catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of pursuing the relative pipe dream of getting a KVPY scholarship for admission to an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo (or two). Thank you for always believing in me and for letting me pursue my passions; I would be nothing without you. 
}
\allowdisplaybreaks %allow align envts to go across pages

>>>>

%The acknowledgements go here.
\acknowledgments{
\vspace{-0.1cm}
First and foremost, I am grateful to my advisors, Prof. Vishwesha Guttal and Prof. Rohini Balakrishnan, for their masterful mentoring. The enormous academic freedom they gave me to pursue essentially whichever ideas seemed promising at the time, coupled with their readiness to provide detailed guidance whenever I asked for it, made working with them an incredibly enriching experience. Their constant focus on the bigger picture was vital to helping me see the forest when I was stuck looking at the trees. Both Vishu and Rohini are brilliant scientists and fantastic mentors, and their mentorship and guidance have deeply impacted my ways of thinking about science and mentoring. I am also grateful to all the members of the \href{https://teelabiisc.wordpress.com/}{Theoretical Ecology and Evolution lab} and the \href{https://sites.google.com/view/rohinibalakrishnanlab/home}{Animal Communication and Bioacoustics Lab} for providing a supportive and productive working environment.

I would also like to thank Prof. Sutirth Dey, my expert for this project. Sutirth provided constructive comments during the mid-year evaluation that helped me re-evaluate my project and its goals. Sutirth's brilliant course on evolution at IISER and various fascinating conversations with him and other lab members during my time as an intern at the \href{https://sites.google.com/a/acads.iiserpune.ac.in/sdlab/pbl-iiser-p}{Population Biology Lab} have been instrumental in shaping my thoughts on evolution. I am also extremely grateful to Dr. Anand Krishnan for constantly supporting me and always being there when I needed advice --- Thank you for everything.

I am grateful to many friends who made the IISER journey enjoyable. Countless long days and nights with Adithyan, Abhishek, Arjun, Chebi, Gaurav, Harshit, Manas, Milie, and Shruthi, have greatly helped me grow as a person, both intellectually and emotionally. Arjun has always been a great sounding board for my thoughts, no matter how inane, and has been very patient and supportive in more ways than I could list here. Milie is the occasional fitness friend that everyone needs, and occasionally texting her encouraged me to hit the gym at least semi-regularly even during hectic parts of the thesis project when schedules were uncertain. I am indebted to our D\&D group in general and Manas in particular for introducing me to D\&D and Critical Role, both of which were very helpful in getting through the pandemic and the thesis year. Shruthi is a constant source of cat related mental health boosts and has more generally taught me a lot about a lot during my time at IISER. I am also grateful to Abhishek for letting me bother him with various physics-related questions throughout the project year. I entered this project as someone who knew some mathematics and some biology but quickly realized I would benefit from reading physics papers (typically written in physics language). Abhishek patiently answered all my basic questions about physics language/tools and skillfully helped me understand how physicists think. Insightful conversations about evolution with Gaurav were formative in gaining fresh perspectives on various topics. Closer to home, Akshay and Prerana have been my closest friends since high school and continue to provide unerring and unconditional love and support. I don't know where I would be without them today.

@@

Finally, I am eternally indebted to my parents, Raja and Vidya. They have unfailingly supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest with no cellular network catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of fully committing to the pipe dream of getting admission in an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo. Thank you for always believing in me and letting me make my own choices; I would be nothing without you. 
}
\allowdisplaybreaks %allow align envts to go across pages
